Astr 513: Homework 2

### 2016-03-09 HW2/HW2.tex
Started writing my sections (d,e). Changed equation* to equaton so that we can reference things if we want to.

\begin{enumerate}[a)]
 \item We can use three kinematic equations to find $u_x$ and $u_y$ in terms of $R$, $g$, and $h$:
 \begin{enumerate}[(1)]
  \item $0 = u_y^2 - 2 g h \Rightarrow \boxed{u_y = \sqrt{2 g h}}$
  \item $0 = u_y - \frac{g t}{2} = \sqrt{2 g h} - \frac{g t}{2} \Rightarrow t = \sqrt{\frac{8 h}{g}}$
  \item $R = u_x t = u_x \sqrt{\frac{8 h}{6}} \Rightarrow \boxed{u_x = R \sqrt{\frac{g}{8h}}}$
 \end{enumerate}
 In the error propagation method, the expected values for $u_x$ and $u_y$ are just the values $u_x^0$ and $u_y^0$ we obtain when we insert the mean values $R_0$, $g_0$, and $h_0$ into the expressions above:
 \begin{subequations}
  \begin{align*}
   u_x^0 &= R_0 \sqrt{\frac{g}{8 h}} \\
   &= 10.0 \mathrm{m} \sqrt{\frac{9.81 \cancel{\mathrm{m}} \cdot \mathrm{s}^{-2}}{8 \cdot 1.0 \cancel{\mathrm{m}}}}
  \end{align*}
  \begin{equation*}
   \boxed{u_x^0 \approx 11.1 \mathrm{m} \cdot \mathrm{s}^{-1}}
  \end{equation*}
 \end{subequations}
 \begin{subequations}
  \begin{align*}
   u_y^0 &= \sqrt{2 g_0 h_0} \\
   &= \sqrt{2 \cdot 9.81 \mathrm{m} \cdot \mathrm{s}^{-2} \cdot 1.0 \mathrm{m}}
  \end{align*}
  \begin{equation*}
   \boxed{u_y^0 \approx 4.43 \mathrm{m} \cdot \mathrm{s}^{-1}}
  \end{equation*}
 \end{subequations}

 When using propagation of errors, the fractional error on some function $f\left(\vec{x}\right)$ with mean $\vec{x}$ values $\vec{x}^0$ and errors $\sigma_i$ can be found by $\frac{\sigma_f}{f} = \sqrt{\displaystyle \sum_{i = 1}^n \left(\frac{\partial \ln f}{\partial x_i}\right)_{\vec{x}^0} \sigma_i^2 }$. So we first take the natural log of $u_x$ and $u_y$:
 \begin{align*}
  \ln u_x &= \ln R + \frac{1}{2} \ln g - \frac{1}{2} \ln h - \frac{3}{2} \ln 2 \\
  \ln u_y &= \ln 2 + \ln g + \ln h
 \end{align*}
 Then we find that
 \begin{subequations}
  \begin{align*}
   \frac{\sigma_{u_x}}{u_x} &= \sqrt{\left(\frac{\sigma_R}{R_0}\right)^2 + \frac{1}{4} \left(\frac{\sigma_g}{g_0}\right)^2 + \frac{1}{4} \left(\frac{\sigma_h}{h_0}\right)^2} \\
   &= \sqrt{\left(\frac{0.2\cancel{\mathrm{m}}}{10.0\cancel{\mathrm{m}}}\right)^2 + \frac{1}{4} \left(\frac{0.05 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}{9.81 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}\right)^2 + \frac{1}{4} \left(\frac{0.2 \cancel{\mathrm{m}}}{1.0 \cancel{\mathrm{m}}}\right)^2}
  \end{align*}
  \begin{equation*}
   \boxed{\frac{\sigma_{u_x}}{u_x} \approx 0.10}
  \end{equation*}
 \end{subequations}
 for $\sigma_{u_x}$, and for $\sigma_{u_y}$,
 \begin{subequations}
  \begin{align*}
   \frac{\sigma_{u_y}}{u_y} &= \sqrt{\frac{1}{4} \left(\frac{\sigma_g}{g_0}\right)^2 + \frac{1}{4} \left(\frac{\sigma_h}{h_0}\right)^2} \\
   &= \frac{1}{2} \sqrt{\left(\frac{0.05 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}{9.81 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}\right)^2 + \left(\frac{0.2 \cancel{\mathrm{m}}}{1.0 \cancel{\mathrm{m}}}\right)^2}
  \end{align*}
  \begin{equation*}
   \boxed{\frac{\sigma_{u_y}}{u_y} \approx 0.10}
  \end{equation*}
 \end{subequations}

@@

\section{Parts D and E}

>>>>

\begin{enumerate}[a)]
 \item We can use three kinematic equations to find $u_x$ and $u_y$ in terms of $R$, $g$, and $h$:
 \begin{enumerate}[(1)]
  \item $0 = u_y^2 - 2 g h \Rightarrow \boxed{u_y = \sqrt{2 g h}}$
  \item $0 = u_y - \frac{g t}{2} = \sqrt{2 g h} - \frac{g t}{2} \Rightarrow t = \sqrt{\frac{8 h}{g}}$
  \item $R = u_x t = u_x \sqrt{\frac{8 h}{6}} \Rightarrow \boxed{u_x = R \sqrt{\frac{g}{8h}}}$
 \end{enumerate}
 In the error propagation method, the expected values for $u_x$ and $u_y$ are just the values $u_x^0$ and $u_y^0$ we obtain when we insert the mean values $R_0$, $g_0$, and $h_0$ into the expressions above:
 \begin{subequations}
  \begin{align*}
   u_x^0 &= R_0 \sqrt{\frac{g}{8 h}} \\
   &= 10.0 \mathrm{m} \sqrt{\frac{9.81 \cancel{\mathrm{m}} \cdot \mathrm{s}^{-2}}{8 \cdot 1.0 \cancel{\mathrm{m}}}}
  \end{align*}
  \begin{equation}
   \boxed{u_x^0 \approx 11.1 \mathrm{m} \cdot \mathrm{s}^{-1}}
  \end{equation}
 \end{subequations}
 \begin{subequations}
  \begin{align*}
   u_y^0 &= \sqrt{2 g_0 h_0} \\
   &= \sqrt{2 \cdot 9.81 \mathrm{m} \cdot \mathrm{s}^{-2} \cdot 1.0 \mathrm{m}}
  \end{align*}
  \begin{equation}
   \boxed{u_y^0 \approx 4.43 \mathrm{m} \cdot \mathrm{s}^{-1}}
  \end{equation}
 \end{subequations}

 When using propagation of errors, the fractional error on some function $f\left(\vec{x}\right)$ with mean $\vec{x}$ values $\vec{x}^0$ and errors $\sigma_i$ can be found by $\frac{\sigma_f}{f} = \sqrt{\displaystyle \sum_{i = 1}^n \left(\frac{\partial \ln f}{\partial x_i}\right)_{\vec{x}^0} \sigma_i^2 }$. So we first take the natural log of $u_x$ and $u_y$:
 \begin{align*}
  \ln u_x &= \ln R + \frac{1}{2} \ln g - \frac{1}{2} \ln h - \frac{3}{2} \ln 2 \\
  \ln u_y &= \ln 2 + \ln g + \ln h
 \end{align*}
 Then we find that
 \begin{subequations}
  \begin{align*}
   \frac{\sigma_{u_x}}{u_x} &= \sqrt{\left(\frac{\sigma_R}{R_0}\right)^2 + \frac{1}{4} \left(\frac{\sigma_g}{g_0}\right)^2 + \frac{1}{4} \left(\frac{\sigma_h}{h_0}\right)^2} \\
   &= \sqrt{\left(\frac{0.2\cancel{\mathrm{m}}}{10.0\cancel{\mathrm{m}}}\right)^2 + \frac{1}{4} \left(\frac{0.05 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}{9.81 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}\right)^2 + \frac{1}{4} \left(\frac{0.2 \cancel{\mathrm{m}}}{1.0 \cancel{\mathrm{m}}}\right)^2}
  \end{align*}
  \begin{equation}
   \boxed{\frac{\sigma_{u_x}}{u_x} \approx 0.10}
  \end{equation}
 \end{subequations}
 for $\sigma_{u_x}$, and for $\sigma_{u_y}$,
 \begin{subequations}
  \begin{align*}
   \frac{\sigma_{u_y}}{u_y} &= \sqrt{\frac{1}{4} \left(\frac{\sigma_g}{g_0}\right)^2 + \frac{1}{4} \left(\frac{\sigma_h}{h_0}\right)^2} \\
   &= \frac{1}{2} \sqrt{\left(\frac{0.05 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}{9.81 \cancel{\mathrm{m}} \cdot \cancel{\mathrm{s}^{-2}}}\right)^2 + \left(\frac{0.2 \cancel{\mathrm{m}}}{1.0 \cancel{\mathrm{m}}}\right)^2}
  \end{align*}
  \begin{equation}
   \boxed{\frac{\sigma_{u_y}}{u_y} \approx 0.10}
  \end{equation}
 \end{subequations}

@@

\section{Part D}
Bayes' Theorem says
\begin{equation}
  P(A|B) = \frac{P(B|A)P(A)}{P(B)}
\end{equation}
where $P(X|Y)$ is a conditional probability of $X$ given $Y$, and $P(Z)$ is 
refered to as a \textit{prior} belief on what the value of $Z$ should be.
Frequentists equate the two conditional probabilities, but this is incorrect
in the Bayesian approach precisely because you wish to be informed by the 
priors. In this part, we assume \textit{uniform} priors on our posterior
parameters $u_x$, $u_y$ and $g$, and in addition to this there is no Jacobian 
transformation. Thus we can write for the conditional probability
\begin{equation}

\end{equation}
